Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-24 acl.2016/acl2016.tex
start acl 2016 paper

A number of the decoders support multithreading whilst others use alternative methods such as Hadoop or external scripts to parallelize decoding. As we shall see in the Results Section, there are severe limitations to parallelizing using a external scripts to exectute multiple decoding processes.

(mtplz) is perhaps closest in intent to this work. It describes a novel

>>>>

A number of the decoders support multithreading whilst others use alternative methods such as Hadoop or external scripts to parallelize decoding. We shall investigate the efficiency of using parallelizing decoding using the multi-processor approach. None of the decoder focus on multi-threads decoding.

Other prior work look to optimizing specific components of decoding. (Liang and Chiang) describes the cube-pruning and cube-growing algorithm for decoding which allows the tradeoff between speed and translation quality to the adjusted with a simgle parameter. (KenLM) and (DALM) describes fast, efficient datastructures for language models. (Zen) describes an implementation of a phrase-table for an SMT decoder that is loaded on demand, reducing the initial loading time and memory requirements. (CompactPT) extends this by compressing the on-disk phrase table and lexicalized re-ordering model resulting in impressive speed gains over previous work.

(mtplz) is perhaps closest in intent to this work. This takes a wholistic approach to decoding, describing a novel decoding algorithm which is fis focused on better decoding speed. It also describes a number of implementation details for faster decoding. However, the decoding algorithm is only able to incorporate one stateful feature function which precludes some of the useful decoding configurations which contains multiple stateful feature functions. It does not include a load-on-demand phrase table, therefore, cannot be used in a commercial environment where phrase-table has not be filtered with a know test set for any realistic size phrase-table. Neither is it multi-threaded.

\section{BLAH BLAH}
